% Overleaf beamerposter template for academic posters
\documentclass[final,t]{beamer}
\mode<presentation>
{
  \usetheme{Berlin}
}
\usepackage[orientation=landscape,size=a0,scale=1.3]{beamerposter}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{tikz}
\usetikzlibrary{shapes,arrows,positioning}
\usepackage{listings}
\usepackage{ragged2e}

% Color scheme
\definecolor{primary}{RGB}{0,123,255}
\definecolor{secondary}{RGB}{108,117,125}
\definecolor{success}{RGB}{40,167,69}
\definecolor{warning}{RGB}{255,193,7}
\definecolor{darkblue}{RGB}{0,86,179}

\setbeamercolor{block title}{fg=white,bg=primary}
\setbeamercolor{block body}{fg=black,bg=white}
\setbeamercolor{structure}{fg=primary}

\title{\LARGE LocalSketch: Peer-to-Peer Collaborative Whiteboard}
% \author{Krishna}
% \institute{DS Final Project --- April 2026}

\begin{document}
\begin{frame}[t]
\begin{columns}[t]

%%%%%%%% COLUMN 1 %%%%%%%%
\begin{column}{.30\linewidth}

\begin{block}{What?}
\textbf{LocalSketch} is a collaborative whiteboard application that works entirely in the browser using peer-to-peer connections. \textbf{No server needed!}

\vspace{0.5cm}
\textbf{Key Features:}
\begin{itemize}
    \item Drawing tools: Freehand, shapes, text
    \item Real-time collaboration
    \item Offline-first with IndexedDB
    \item Room-based sessions
    \item Undo/Redo support
\end{itemize}
\end{block}

\vspace{0.5cm}

\begin{block}{Why?}
\textbf{Privacy \& Control}\\
Traditional tools (Google Docs, Figma, Miro) send all your data through their servers. \textbf{LocalSketch keeps your data on your device} - it only syncs directly with peers you choose.

\vspace{0.5cm}
\textbf{Resilient to Network Issues}\\
Works offline and automatically syncs when connection returns. Perfect for unreliable networks!

\vspace{0.5cm}
\textbf{Learning Experience}\\
Fun exploration of:
\begin{itemize}
    \item \textbf{CRDTs} (Conflict-free Replicated Data Types)
    \item \textbf{WebRTC} for peer-to-peer networking
    \item \textbf{Local-first software} principles
\end{itemize}
\end{block}

\vspace{0.5cm}

\begin{block}{How? Architecture}
\begin{center}
\begin{tikzpicture}[node distance=2cm,
    box/.style={rectangle, draw=primary, fill=blue!10, text width=4.55cm, align=center, rounded corners, minimum height=1.3cm, thick}]
    
    \node[box] (react) {React + TypeScript\\UI Layer};
    \node[box, below=1.5cm of react] (yjs) {Yjs Document\\CRDT State};
    \node[box, below left=1.2cm and 0.5cm of yjs] (indexdb) {IndexedDB\\Persistence};
    \node[box, below right=1.2cm and 0.5cm of yjs] (webrtc) {WebRTC\\P2P Sync};
    
    \draw[->, thick, primary] (react) -- (yjs);
    \draw[<->, thick, primary] (yjs) -- (indexdb);
    \draw[<->, thick, primary] (yjs) -- (webrtc);
\end{tikzpicture}
\end{center}

\vspace{0.5cm}
\textbf{Key Technical Decisions}

\textbf{1. Yjs for State Management}
\begin{itemize}
    \item Y.Map stores all strokes with unique IDs
    \item Y.Array for stroke points
    \item Built-in conflict resolution!
\end{itemize}

\vspace{0.3cm}
\textbf{2. Transform-based Editing}

Each stroke stores: type, points, color, offsetX/Y, scaleX/Y for non-destructive transformations!

\vspace{0.3cm}
\textbf{3. WebRTC with STUN/TURN}
\begin{itemize}
    \item Direct P2P when possible
    \item TURN relay fallback
    \item Signaling server for handshake only
\end{itemize}
\end{block}

\end{column}

%%%%%%%% COLUMN 2 %%%%%%%%
\begin{column}{.38\linewidth}

\begin{block}{\LARGE Main Finding}
\begin{center}
\vspace{1cm}
{\Huge \textbf{Real-time collaboration}}\\[0.5cm]
{\Huge \textbf{WITHOUT SERVERS!}}

\vspace{1cm}
{\LARGE LocalSketch uses \textbf{WebRTC + Yjs} to enable}\\
{\LARGE peer-to-peer collaborative drawing that works}\\
{\LARGE \textbf{offline} and syncs instantly when reconnected.}

\vspace{1cm}
\colorbox{primary!20}{
\parbox{0.9\linewidth}{
\centering
\Large
\textbf{Local-first architecture}\\[0.3cm]
Your data stays on your device\\[0.5cm]
\textbf{Peer-to-Peer networking}\\[0.3cm]
Direct connections, no middleman\\[0.5cm]
\textbf{Works offline}\\[0.3cm]
Syncs when you reconnect\\[0.5cm]
\textbf{CRDTs handle conflicts}\\[0.3cm]
Automatic merge, always
}
}
\vspace{1cm}
\end{center}
\end{block}

\vspace{0.5cm}

\begin{block}{Challenges \& Solutions}
\colorbox{blue!10}{
\parbox{0.95\linewidth}{
\textbf{Problem:} Canvas state not syncing when new peer joins\\
\textbf{Solution:} Wait for IndexedDB to load before WebRTC

\vspace{0.2cm}
\texttt{\small
indexDB.once('synced', () => \{\\
~~webrtc = new WebrtcProvider(...)\}
);
}
}
}

\vspace{0.5cm}
\colorbox{blue!10}{
\parbox{0.95\linewidth}{
\textbf{Problem:} Resizing distorted stroke thickness\\
\textbf{Solution:} Scale-compensated line width

\vspace{0.2cm}
\texttt{\small
const maxScale = Math.max(\\
~~Math.abs(scaleX), Math.abs(scaleY)\\);\\
ctx.lineWidth = 4 / maxScale;
}
}
}

\vspace{0.5cm}
\colorbox{blue!10}{
\parbox{0.95\linewidth}{
\textbf{Problem:} Erase tool needs to account for transforms\\
\textbf{Solution:} Reverse-transform mouse coordinates before hit-testing
}
}
\end{block}

\end{column}

%%%%%%%% COLUMN 3 %%%%%%%%
\begin{column}{.30\linewidth}

\begin{block}{What Works?}
\textbf{Core Functionality}
\begin{itemize}
    \item Multiple drawing tools with color selection
    \item Select, move, and resize any shape
    \item Undo/Redo (Y.UndoManager)
    \item Real-time multi-user collaboration
    \item Offline persistence and sync
\end{itemize}

\vspace{0.3cm}
\textbf{Network Resilience}
\begin{itemize}
    \item Works completely offline
    \item Auto-reconnects when network returns
    \item Peer count display shows connection status
    \item Data persists across sessions
\end{itemize}

\vspace{0.3cm}
\textbf{Demo Stats (3 users)}
\begin{itemize}
    \item \textbf{Sync latency:} 50-200ms (local network)
    \item \textbf{Conflict resolution:} Automatic (CRDT magic!)
    \item \textbf{Data size:} $\sim$100 strokes = $\sim$50KB in IndexedDB
    \item \textbf{Merge conflicts:} 0
\end{itemize}
\end{block}

\vspace{0.5cm}

\begin{block}{Limitations \& Future Work}
\textbf{Current Limitations}
\begin{itemize}
    \item \textbf{No persistent server:} Rooms only exist while peers online
    \item \textbf{NAT traversal:} May fail on restricted networks without TURN
    \item \textbf{No authentication:} Anyone with room name can join
    \item \textbf{Canvas size:} Fixed dimensions (not infinite)
\end{itemize}

\vspace{0.3cm}
\textbf{What I'd Do Next}
\begin{itemize}
    \item \textbf{Infinite canvas:} Pan/zoom like Miro
    \item \textbf{More tools:} Pen pressure, layers, images
    \item \textbf{Hybrid sync:} Optional server for persistence
    \item \textbf{Export:} Save as PNG/SVG
    \item \textbf{Performance:} Optimize for 1000+ strokes
\end{itemize}
\end{block}

\vspace{0.5cm}

\begin{block}{Key Takeaways}
\textbf{What I Learned}
\begin{enumerate}
    \item \textbf{CRDTs are powerful:} Yjs handles all merge complexity
    \item \textbf{WebRTC is tricky:} NAT traversal needs careful setup
    \item \textbf{Local-first is viable:} Great UX for collaborative apps
    \item \textbf{Transform-based editing:} Cleaner than re-calculating geometry
\end{enumerate}

\vspace{0.3cm}
\textbf{Would I Recommend This Approach?}

\colorbox{success!20}{
\parbox{0.95\linewidth}{
\textbf{YES, if:}
\begin{itemize}
    \item Privacy is important
    \item Offline functionality required
    \item Small groups (< 20 users)
\end{itemize}
}
}

\vspace{0.3cm}
\colorbox{warning!30}{
\parbox{0.95\linewidth}{
\textbf{NO, if:}
\begin{itemize}
    \item Need persistent storage
    \item Large-scale collaboration
    \item Strict access control required
\end{itemize}
}
}
\end{block}

\vspace{0.5cm}

\begin{block}{Tech Stack}
React 19 • TypeScript • Vite • Yjs 13.6 • y-webrtc • y-indexeddb • WebRTC • IndexedDB
\end{block}

\end{column}

\end{columns}
\end{frame}
\end{document}
